BLUP anaysis

### 2020-04-29 R/rrBLUP_analysis_D2F.Rmd
rrBLUP and h^2 analysis for D2F

@@

@@

>>>>

cov

@@

```{r}
phe_all %>% left_join(metadata) %>%
  pivot_longer(values_to = "MEAS", cols = TC_EOS:GR50, names_to = "PHE") %>%
  dplyr::select(-LIBRARY, -(GENETIC_SUBPOP_KINSHIP:PLANTED_2018)) %>%
  filter(SUBPOP %in% c("Gulf", "Midwest", "Atlantic")) %>%
  group_by(SUBPOP, SITE, PHE) %>%
  summarise(X_bar = mean(MEAS, na.rm = TRUE),
            V_P = var(MEAS, na.rm = TRUE),
            I = V_P / X_bar^2, 
            CV_P = 100*sqrt(V_P) / X_bar) %>%
  arrange(PHE, SITE, SUBPOP)

@@

# Per subpop analysis

  testdf <- phe_all %>%
    left_join(metadata) %>%
    filter(!is.na(eval(PHE[[i]])) & GENETIC_SUBPOP_KINSHIP %in% c("Midwest")) %>%
    as.data.frame()

  saveRDS(bluprrk, paste0("~/Github/pvdiv-phenology-gxe/data-raw/ignore/", 
                          PHE[[i]],
                          "_134g_Midwest_10Site_BLUPs_kinship.rds"))
}
```

```{r}
BLUPs <- select(metadata, PLANT_ID, SUBPOP) %>%
  filter(SUBPOP %in% c("Midwest")) %>%
  left_join(dplyr::select(kinseqblup[[1]], PLANT_ID, 3))

BLUPtable
phe_all %>% left_join(metadata) %>%
  pivot_longer(values_to = "MEAS", cols = TC_EOS:GR50, names_to = "PHE") %>%
  dplyr::select(-LIBRARY, -(GENETIC_SUBPOP_KINSHIP:PLANTED_2018)) %>%
  filter(SUBPOP %in% c("Midwest")) %>%
  group_by(PHE) %>%
  summarise(X_bar = mean(MEAS, na.rm = TRUE),
            V_P = var(MEAS, na.rm = TRUE),
            I = V_P / X_bar^2, 
            CV_P = 100*sqrt(V_P) / X_bar) %>%
  arrange(desc(I)) %>%
  full_join(BLUPtable, by = c("PHE" = "Phenotype")) %>%
  mutate(I_A = V_a / X_bar^2,
         CV_R = 100 * sqrt(V_P - V_a) / X_bar, 
         CV_A = 100 * sqrt(V_a) / X_bar,
         CV_E = 100 * sqrt(V_e) / X_bar) %>%
  write_csv(., "~/Github/pvdiv-phenology-gxe/data-raw/ignore/Phenotypic_CVs_10_site_fixed_effects_134g_Midwest.csv")
```
